Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-15 WSSSPE2_report/WSSSPE2_review.tex
adding some authors

\author{TBD by contributions \\{\scriptsize\today \quad  (Due:  $\backsim$ April 30)}} 
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$,
%Richard Littauer$^{(9)}$,
%Miguel de Val-Borro$^{(10)}$, 
%Sou-Cheng T. Choi$^{(11)}$}
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}

>>>>

\author{Daniel S. Katz$^{(1)}$, Sou-Cheng T. Choi$^{(11)}$, Nancy Wilkins-Diehr$^{(8)}$, Neil Chue Hong$^{(3)}$, \\
James Howison  (affil etc. needed), Miguel de Val-Borro (affill etc. needed), Richard Littauer (affil etc. needed) \\
more TBD by contributions \\
{\scriptsize\today \quad  (Due:  $\backsim$ April 30)}} 
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$,  \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$,
%Richard Littauer$^{(9)}$,
%Miguel de Val-Borro$^{(10)}$, 
%Sou-Cheng T. Choi$^{(11)}$}
%
\thanks{{}$^{(1)}$ Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
\thanks{{}$^{(11)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA}
